Ecological network control

### 2018-05-11 paper/supp-info.Rmd
Describe structural controllability in the supp info

>>>>

# Structural controllability {#structural-controllability}

Structural controllability avoids the limitation of not knowing the exact values of the matrices *A* and *B*. 
The graphical interpretation of structural controllability can be summed up in two conditions for controllability: A system is controllable if there are no inaccessible nodes or dilations. A node is inaccessible if there are no directed paths between it and the input nodes. "Dilations are subgraohs in which a small subset of nodes attempts to rule a larger subset of nodes. In other workds there are more 'subordinates' than 'superiors'" [@liu_control_2016].

The goal of structural controllability is to use the information contained in **A** to generate a supportable estimate of **B**.
This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised. 
The trade-off of this approach is that, because of the assumption of linearity, structural controllability alone does not allow us to fully design the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another. 
Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for eventually understanding nonlinear control [@liu_controllability_2011; @liu_control_2016].

# Maximum matching

Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-direction-of-control)b). 
Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side. 
To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
Once we have the matching (shown in the Figure \@ref(fig:fig-direction-of-control)b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched. 
This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
Figure \@ref(fig:fig-direction-of-control)d--f illustrate this approach for a network with bidirectional links.

## Finding a single maximum matching {#one-maximum-matching}

## Finding all possible maximum matchings

## Finding all possible minimum driver node sets

# Empirical vs. random expectation of controllability {#randomisations}
